---
title: "Milestone 5"
author: "Hannah Valencia"
date: "3/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(haven)
library(ggplot2)
library(dplyr)
library(readxl)
library(tidyverse)
```

```{r ImportExcel, message = FALSE, warning = FALSE}

# Setting message = FALSE because it is telling us about renaming the columns when we first load in the data, but we are going to be changing these names anyways.
# Setting warning = FALSE because a warning appears about the date format.
# Reading in the excel sheet.

google <- read_xlsx("dataverse_files/Google Trends data for Figure 1.xlsx", 
    col_types = c("date", "numeric", "numeric"))

# Removing two rows that are either empty or are just describing the data set.

google <- google[-c(1, 2),]

# Chnaging the column titles to the first row's information.

colnames(google) = google[1, ]
google = google[-1, ]

colnames(google)[1:3] <- c("week", "clean_gun", "buy_gun")

google$week <- as.Date(google$week , format = "%Y-%m-%d")
```

```{r}
shift_axis <- function(p, y=0){
  g <- ggplotGrob(p)
  dummy <- data.frame(y=y)
  ax <- g[["grobs"]][g$layout$name == "axis-b"][[1]]
  p + annotation_custom(grid::grobTree(ax, vp = grid::viewport(y=1, height=sum(ax$height))), 
                        ymax=y, ymin=y) +
    geom_hline(aes(yintercept=y), data = dummy) +
    theme(axis.text.x = element_blank(), 
          axis.ticks.x=element_blank())

}
```

```{r}
rects <- data.frame(xstart = as.POSIXct('2012-12-14'), xend = as.POSIXct('2013-04-14'))
```

```{r}
plot <- google %>%
  ggplot(aes(x = week)) +
  geom_line(aes(y = clean_gun), color = "black") +
  geom_line(aes(y = buy_gun), color = "red") +
  annotate("rect", xmin = as.Date('2012-12-14'), xmax = as.Date('2013-04-14'), ymin = 0, ymax = Inf, alpha = 0.2) +
  scale_x_date(date_breaks = "1 year", date_minor_breaks = "1 month", date_labels = "%Y") +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80, 100, 120), limits = c(0, 120)) +
  labs(x = "", y = "Index Value (100 = maximum)") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line( size=0.3, color = "darkgray"),
        panel.background = element_rect(fill= "white")) +
  annotate(geom = "text", x = as.Date('2013-11-15'), y = 96, label = "Post-Sandy Hook Window", size = 3) +
  annotate(geom = "text", x = as.Date('2010-06-15'), y = 56, label = "'Clean Gun' (black line)", size = 3) +
  annotate(geom = "text", x = as.Date('2010-05-15'), y = 11.5, label = "'Buy Gun' (red line)", size = 3)

shift_axis(plot, 0)
```


**Fig. 1. Relative frequency of weekly Google searches that included the terms “clean gun” and
“buy gun” between 2010 and 2014.** This graph uses data from Google Trends (http://trends.
google.com/) to track weekly patterns in search activity that included each set of words. The week
with maximum search volume is indexed to equal 100 and values below 100 reflect relative search
activity in proportion to the week with the maximum value.

























